Formation of porous crystals via viscoelastic phase separation

### 2016-12-20 nature/Supplementary.tex
Dear all,
I have made corrections associated with new Supplementary Movie 3. 
Please check them. 

If you agree with the inclusion of new Movie 3, I think that we are ready to resubmission!

How do you think?

Best wishes, 
Hajime
Merge movies 1 and 2 Rename 3 as 2

\centerline{\bf \large Supplementary Information for}
\centerline{\bf \large``A novel route to the spontaneous formation of porous crystals via}
\centerline{\bf \large viscoelastic phase separation''}
\vspace{0.5cm}

@@

\bibliographystyle{naturemag2}
\bibliography{biblio}

@@

\section*{Supplementary Movie 1}
This movie shows the early stage of gelation process of $\phi\approx 0.30$ and $c_p=0.38$ mg/g, from the original confocal images at the same z-position as Fig.~3a. Total duration is 1160 s (530~$\tau$). We quickly started scanning the sample after exchanging the salt-reservoir with the solvent including salt. At the beginning, salt had not reached the scanning volume and colloids were dispersed by electrostatic repulsion. At 0:02 in the movie, salt diffused into the scanning volume and screened the surface charges of colloids. Then, colloids immediately initiated phase separation by short-ranged attractions.

\section*{Supplementary Movie 2}
This movie shows the late stage after Supplemental Movie 1 with scanning duration of 27000~s (12300~$\tau$). 
Please note that there is a large difference in the frame rate between Movie 1 and 2.

\section*{Supplementary Movie 3}
Same as Supplementary Movie 2, but with computer rendered trajectories obtained from the tracking of the colloidal particles.
Particles are colored according to the following code: crystal (red), surface (blue), gas (green) and liquid (white).
For display purposes, crystalline particles and gas particles are respectively 400\% and 50\% bigger than other particles (liquid or surface).

>>>>

\centerline{\bf \large Supplementary Information for}
\centerline{\bf \large``Formation of porous crystals via viscoelastic phase separation'' }
\vspace{0.5cm}

@@

%\clearpage
\bibliographystyle{naturemag2}
\bibliography{biblio}

@@

\section*{Supplementary Movie 1}
This movie shows the gelation process of $\phi\approx 0.30$ and $c_p=0.38$ mg/g, from the original confocal images at the same z-position as Fig.~4d. As stressed by the time stamps, we use two very different frame rates for the first 12~s of the movie (1160~s in real time or 530~$\tau_B$) and the remaining 15~s (27000~s in real time or 12300~$\tau_B$). We quickly started scanning the sample after exchanging the salt-reservoir with the solvent including salt. At the beginning, salt had not reached the scanning volume and colloids were dispersed by electrostatic repulsion. At time stamp $t=0$, salt diffused into the scanning volume and screened the surface charges of colloids. Then, colloids immediately initiated phase separation by short-ranged attractions. At later times crystalline order is visible.

\section*{Supplementary Movie 2}
Same as the end of Supplementary Movie 1, but with computer rendered trajectories obtained from the tracking of the colloidal particles. Particles are coloured according to the following code: crystal (red), surface (blue), gas (green) and liquid (white). For display purposes, crystalline particles and gas particles are respectively 400\% and 50\% bigger than other particles (liquid or surface).
